\textbf{\sc Towards Deliberative Control of Autonomous Robots}

### 2012-01-30 future.tex
updates

% multi-vehicle control
% sampling
% diagnosis and recovery
feature recognition
scalable architecture for missions

>>>>

Feature recognition for Sampling is a general research thrust; however
it has specific relevance in the context of \rx and AUV control. As
noted in Section \ref{sec:results} we have already demonstrated
Machine Learning techniques for recognition of select features in the
coastal ocean. A principal challenge that remains is that of obtaining
expert labeled data for any supervised or semi-supervised learning
methods.  While supervised techniques for learning classifiers such as
decision trees (\cite{Quinlan93-dtrees}), instance-based
classification (\cite{Aha-ibl-ml91}), Bayesian classifiers
(\cite{Jensen2001-BNetworks}) and artificial neural networks
(\cite{ANNsurvey-2000}) are popular, given the vast amount of data
available and poor understanding of correlation between physical and
biogeochemical variables in the coastal ocean, our work on INLs
\cite{mcgann08d,ryan10} and reliance on a oceanographic expert has
shown that scaling to different problems remains problematic. This is
a prime motivation to move towards more semi-supervised methods such
as \cite{kumar11,sergio12}. With the advent of the \od however,
another direction our research is taking us is in Recommender systems
\cite{Adomavicius05} as noted in Section \ref{sec:results}. We are
working to design and deploy software infrastructure that will learn
from user tagged data. To do so, we will use tagging techniques
similar to what users of commercial image sharing sites like Flickr
and Picassa do, to learn the context of the data (including remote
sensing). In addition, the \od will integrate statistical Machine
Learning techniques with incoming asynchronous data stream obtained by
sensors and platforms. Identification models will be based on existing
training sets for INLs and plumes; models for other features of
scientific interests driven by \can requirements will be built in
addition. Existing AUV archives for instance provide sufficient data
for a learning base for a range of features of interest to \can; in
addition we will build software that will learn to incorporate
incoming data streams to provide an existence proof of a feature of
interest.

% multi-vehicle control
% sampling
% diagnosis and recovery
% feature recognition
% scalable architecture for missions

### 2012-01-30 results.tex
updates

Additionally, our work on \od is driven by a vision of how marine
field robotics will likely be conducted in the future and the
necessary computational infrastructure that will augment decision
making, onshore as well as on-board. We believe ultimately \od will
combine capabilities inferential and data gathering and analysis
capabilities and more uniquely, provide an event response capability
that could trigger the deployment of a robot and/or adapt its sampling
strategy, all from a scientist's desktop on shore. Data returned from
robotic assets at sea will be filtered for signals associated with
feature(s) of interest along with information on its contextual
environment. The association between the signal and a prospective
event will be undertaken through tagging by experts and machine
learning techniques used in recommender
systems\cite{Adomavicius05}. Adaptive sampling strategies will then
balance decision-making \situ with that done onshore with
computational models and human agents, the subject of a new NSF
project in which the authors are participating.

>>>>

Additionally, our work on \od is driven by a vision of how marine
field robotics will likely be conducted in the future and the
necessary computational infrastructure that will augment decision
making, onshore as well as on-board. We believe ultimately \od will
combine capabilities inferential and data gathering and analysis
capabilities and more uniquely, provide an event response capability
that could trigger the deployment of a robot and/or adapt its sampling
strategy, all from a scientist's desktop on shore. Data returned from
robotic assets at sea will be filtered for signals associated with
feature(s) of interest along with information on its contextual
environment. The association between the signal and a prospective
event will be undertaken through tagging by experts and machine
learning techniques used in recommender systems
\cite{Adomavicius05}. Adaptive sampling strategies will then balance
decision-making \situ with that done onshore with computational models
and human agents, the subject of a new NSF project in which the
authors are participating.
